Multiple Kernelized Correlation Filters based High Speed Target Following

### 2017-04-11 draft.tex

To train a (binary) classifier to detect the target at every frame,
the classifier needs positive and negative examples. In a typical set
up, a positive example is assumed to be given whereas a set of
negative examples can be randomly collected from the background around
the given positive example. Such a typical setup for a
tracking-by-detection method might have two issues related to its
performance: Firstly, the appearance of the randomly sampled negative
examples might be highly correlated with that of positive one,
resulting in ambiguous boundary between positive and negative
classes. Secondly for a real-time tracking, such a setup would not be
feasible for the practice because the number of training data
gradually increases. Due to these issues, most of the
tracking-by-detection methods focus on efficiently handling
incremental update of the learned classifier and on collecting a
small, but informative negative examples.
\begin{comment}
However, there can be two issues in this framework. First,
the randomly collected samples can have large correlation resulting in
a weak classifier. Also, such framework is not feasible for real-time
tracking as the number of samples gradually increases. Most of the
tracking-by-detection algorithms focus on efficient incremental update
of a classifier together with more useful background sampling.
\end{comment}

@@

Frequency domain correlation filter based trackers in the
tracking-by-detection paradigm has recently seen growing popularity
due to its superior computation and robustness to geometric and
photometric variations. The first correlation filter tracker proposed
by \cite{bolme2010visual} focused on learning and detection in the
frequency domain. The idea was to minimize the sum of squared error in
the frequency domain. Hence, the convolution in the original domain is
avoided, instead, element-wise multiplication is needed in the
frequency domain. This way, it achieved promising performance at 700
Hz. On the other hand, the MOSSE tracker failed in cases with rapidly
changing background as it learns the filter using a single template
and accommodates single channel features. Later on, the MOSSE tracker
was improved by using the circularly shifted background patches in an
efficient way by utilizing the theorem that Discrete Fourier Transform
of a circulant matrix gives us diagonalized circulant matrix
\cite{henriques2012exploiting,henriques2015high}. In the same work,
the authors integrated kernelization concept into the detection and
learning steps to improve tracking
accuracy. \cite{galoogahi2013multi,henriques2015high} extended the
correlation filter trackers with single channel features to
multi-channel features. They employed the color and shape features in
a simple framework by summing the correlation of the test and learned
feature channels elements. There a few major drawbacks of the
correlation filter trackers although they outperformed the other
discriminative trackers with superior computation. First, due to the
nature of correlation filters it is limited to a region of interest
which is typically 2-3 times larger than the target. Considering a
larger ROI not only increases the computational burden but also leads
to further spatial information loss with the fixed template size. For
this reason, its performance degrades in fast motion cases as the ROI
may not contain the target. Second, the correlation filter lacks scale
adaptation ability since it only estimates the translation of the
target. Later studies focused on improving the latter issue by
proposing scale candidates where each scale is assigned a confidence
by performing detection on the shrinked or enlarged the ROI
\cite{li2014scale,tang2015multi,bibi2015multi,ma2015long}. Another
group of studies employ the part-based correlation filter trackers to
better adapt to the scale changes
\cite{liu2015real,akin2016deformable}. The sensitivity to fast motion
is generally handled in the long-term target tracking framework where
track reinilization module is triggered when the target is lost
\cite{ma2015long,de2015board,li2016monocular}.

>>>>

To train a (binary) classifier to detect the target at every frame,
the classifier needs positive and negative examples. In a typical set
up, a positive example is assumed to be given whereas a set of
negative examples can be randomly collected from the background around
the given positive example. Such a typical setup for a
tracking-by-detection method might have two issues related to its
performance: Firstly, the appearance of the randomly sampled negative
examples might be highly correlated with that of positive one,
resulting in ambiguous boundary between positive and negative
classes. Secondly for a real-time tracking, such a setup would not be
feasible for the practice because the number of training data
gradually increases. Due to these issues, most of the
tracking-by-detection methods focus on efficiently handling
incremental update of the learned classifier and on collecting a
small, but informative negative examples.

{\it Burak: Why do we even mention these issues? Is this somehow
  related to what we did for this paper?}

\begin{comment}
However, there can be two issues in this framework. First,
the randomly collected samples can have large correlation resulting in
a weak classifier. Also, such framework is not feasible for real-time
tracking as the number of samples gradually increases. Most of the
tracking-by-detection algorithms focus on efficient incremental update
of a classifier together with more useful background sampling.
\end{comment}

@@

An object tracking method based on the correlation filter in frequency
domain has gained attention due to its fast computation.

\begin{comment}
{\it Burak: This is not entirely true. If this is the case, people
  including us don't have to invent their own, other than just using
  KCF.}

Frequency domain correlation filter based trackers in the
tracking-by-detection paradigm has recently seen growing popularity
due to its superior computation and robustness to geometric and
photometric variations. 
\end{comment}

The first correlation filter tracker proposed by
\cite{bolme2010visual} focused on learning and detection in the
frequency domain. The idea was to minimize the sum of squared error in
the frequency domain. Hence, the convolution in the original domain is
avoided, instead, element-wise multiplication is needed in the
frequency domain. This way, it achieved promising performance at 700
Hz. On the other hand, the MOSSE tracker failed in cases with rapidly
changing background as it learns the filter using a single template
and accommodates single channel features. Later on, the MOSSE tracker
was improved by using the circularly shifted background patches in an
efficient way by utilizing the theorem that Discrete Fourier Transform
of a circulant matrix gives us diagonalized circulant matrix
\cite{henriques2012exploiting,henriques2015high}. In the same work,
the authors integrated kernelization concept into the detection and
learning steps to improve tracking
accuracy. \cite{galoogahi2013multi,henriques2015high} extended the
correlation filter trackers with single channel features to
multi-channel features. They employed the color and shape features in
a simple framework by summing the correlation of the test and learned
feature channels elements. There a few major drawbacks of the
correlation filter trackers although they outperformed the other
discriminative trackers with superior computation. First, due to the
nature of correlation filters it is limited to a region of interest
which is typically 2-3 times larger than the target. Considering a
larger ROI not only increases the computational burden but also leads
to further spatial information loss with the fixed template size. For
this reason, its performance degrades in fast motion cases as the ROI
may not contain the target. Second, the correlation filter lacks scale
adaptation ability since it only estimates the translation of the
target. Later studies focused on improving the latter issue by
proposing scale candidates where each scale is assigned a confidence
by performing detection on the shrinked or enlarged the ROI
\cite{li2014scale,tang2015multi,bibi2015multi,ma2015long}. Another
group of studies employ the part-based correlation filter trackers to
better adapt to the scale changes
\cite{liu2015real,akin2016deformable}. The sensitivity to fast motion
is generally handled in the long-term target tracking framework where
track reinilization module is triggered when the target is lost
\cite{ma2015long,de2015board,li2016monocular}.
